### 2025-09-23 paper/sec/authoring-workflow.tex
First cut of authoring workflow -- bit verbose.

\item \textbf{Manual validation step.} Once a candidate expression has been generated, the author is able to
republish the web page containing the Fluid article and interact with the fragment of text.  As shown in
\secref{}, this is an important validation step that can reveal errors in the generated expression. If the
interactions look reasonable, the author can approve the replacement of the selected substring $s$ with the
interpolation expression \kw{\{$e$\}}, creating a new document configuration. This is the primary successful
path through the workflow and returns the system to the entry state where it is waiting for another top-level
interaction from the author. Otherwise, the author can reject the proposed change and return to the start
state.

>>>>

\item \textbf{Manual validation step.} Once a candidate expression has been generated, the system replaces the
selected substring $s$ with the interpolation expression \kw{\{$e$\}}, creating a new (but only tentative)
document configuration. The author can republish the web page hosting the document and interact with the
proposed revision. As shown in \secref{}, this is an important validation step that can reveal errors in the
generated expression. If the interactions look reasonable, the author can approve the new document state; this
is the primary successful path through the workflow and returns the system to the entry state where it is
waiting for another top-level interaction from the author. Otherwise, the author rejects the proposed change
and returns to the entry state without any change to the document.
